NLTK: The Natural Language Toolkit

### 2004-05-01 technical/acl2004/acl04.tex
final polishing
svn/trunk@1783

\author{
  Steven Bird \\
  Department of Computer Science \\
  \indent and Software Engineering \\
  University of Melbourne \\
  Victoria 3010, Australia \\  
  {\tt sb@csse.unimelb.edu.au}
\And
  Edward Loper\\
  Department of Computer \\
  \indent and Information Science \\
  University of Pennsylvania\\
  Philadelphia PA 19104-6389, USA\\
  {\tt edloper@gradient.cis.upenn.edu}
}

@@

\textbf{Projects.}  NLTK provides students with a flexible framework
for advanced projects.  Typical projects might involve implementing a
new algorithm, developing a new component, or adding support for a new
task.

We chose Python because it has a shallow learning curve, its syntax
and semantics are transparent, and it has good string-handling
functionality.  As an interpreted language, Python facilitates
interactive exploration.  As an object-oriented language, data and
methods can be encapsulated easily.  Python comes with an extensive
standard library, including tools for graphical programming and
intensive numerical processing.  And the recently added generator
syntax makes it easy to create interactive implementations of
algorithms \cite{Loper04,Rossum03intro,Rossum03ref}.

@@

In general, language processing tasks are formulated as
annotations and transformations involving \object{Tokens}.  In
particular, each processing task takes a token, and extends it to
include new information.  Typically, these modifications are
\emph{monotonic}; in other words, new information is added but
existing information is not deleted or modified.  Thus, tokens serve
as a \emph{blackboard}, where information about a piece of text is
collated.  This architecture contrasts with the more typical
\emph{pipeline} architecture, where each processing task's output
discards its input information.  We chose the ``blackboard'' approach
over the ``pipeline'' approach because it allows more flexibility when
combining tasks into a single system.

In addition to the \object{Token} class and its derivatives, NLTK
defines a variety of other data types.  For instance, the
\object{nltk.probability} module defines classes for
probability distributions and statistical smoothing techniques; and
the \object{cfg} module defines classes for encoding context free
grammars and probabilistic context free grammars.

@@

Many language processing tasks must be developed and tested using
annotated data sets, or corpora.  Several such corpora are distributed
with NLTK, as listed in Table~\ref{tab:data}.  The NLTK
\object{corpus} module defines classes for reading and processing
many of these corpora.  The following code fragment illustrates
how the Brown Corpus is accessed.

@@

Each processing module defines an \emph{interface} for its task.
Interface classes are distinguished by naming them with a trailing
capital ``\object{I},'' such as \object{ParserI}.
Each interface defines a single \emph{action method}, which actually
performs the task defined by the interface.  For example, the
\object{ParserI} interface defines the \object{parse} method; and the
\object{Tokenizer} interface defines the \object{tokenize} method.
When appropriate, an interface defines \emph{extended action
  methods}, which provide variations on the basic action method.  For
example, the \object{ParserI} interface defines the \object{parse\_n}
method, which finds at most $n$ parses for a given sentence; and
the \object{TokenizerI} interface defines the \object{xtokenize}
method, which outputs an iterator over subtokens instead of a list of
subtokens.

@@

NLTK is a broad-coverage toolkit that provides a simple, extensible,
uniform framework for assignments, demonstrations and projects.  It is
thoroughly documented, easy to learn, and simple to use.  Readers who
would like to receive occasional announcements about NLTK are
encouraged to sign up for the low-volume, moderated mailing list
\textit{NLTK-Announce}\footnote{\url{http://lists.sourceforge.net/lists/listinfo/nltk-announce}}.

@@

We are indebted to our students for feedback on the toolkit, and to
many contributors listed on the NLTK website.

>>>>

\author{
  Steven Bird \\
  Department of Computer Science \\
  \indent and Software Engineering \\
  University of Melbourne \\
  Victoria 3010, Australia \\  
  {\tt\small sb@csse.unimelb.edu.au}
\And
  Edward Loper\\
  Department of Computer \\
  \indent and Information Science \\
  University of Pennsylvania\\
  Philadelphia PA 19104-6389, USA\\
  {\tt\small edloper@gradient.cis.upenn.edu}
}

@@

\textbf{Projects.}  NLTK provides students with a flexible framework
for advanced projects.  Typical projects might involve implementing a
new algorithm, developing a new component, or implementing a new
task.

We chose Python because it has a shallow learning curve, its syntax
and semantics are transparent, and it has good string-handling
functionality.  As an interpreted language, Python facilitates
interactive exploration.  As an object-oriented language, data and
methods can be encapsulated and re-used easily.  Python comes with an extensive
standard library, including tools for graphical programming and
numerical processing.  And the recently added generator
syntax makes it easy to create interactive implementations of
algorithms \cite{Loper04,Rossum03intro,Rossum03ref}.

@@

In general, language processing tasks are formulated as
annotations and transformations involving \object{Tokens}.  In
particular, each processing task takes a token and extends it to
include new information.  These modifications are typically
\emph{monotonic}; in other words, new information is added but
existing information is not deleted or modified.  Thus, tokens serve
as a \emph{blackboard}, where information about a piece of text is
collated.  This architecture contrasts with the more typical
\emph{pipeline} architecture, where each processing task's output
discards its input information.  We chose the ``blackboard'' approach
over the ``pipeline'' approach because it allows more flexibility when
combining tasks into a single system.

In addition to the \object{Token} class and its derivatives, NLTK
defines a variety of other data types.  For instance, the
\object{probability} module defines classes for
probability distributions and statistical smoothing techniques; and
the \object{cfg} module defines classes for encoding context free
grammars and probabilistic context free grammars.

@@

Many language processing tasks must be developed and tested using
annotated data sets, or corpora.  Several such corpora are distributed
with NLTK, as listed in Table~\ref{tab:data}.  The
\object{corpus} module defines classes for reading and processing
many of these corpora.  The following code fragment illustrates
how the Brown Corpus is accessed.

@@

Each processing module defines an \emph{interface} for its task.
Interface classes are distinguished by naming them with a trailing
capital ``\object{I},'' such as \object{ParserI}.
Each interface defines a single \emph{action method} which
performs the task defined by the interface.  For example, the
\object{ParserI} interface defines the \object{parse} method and the
\object{Tokenizer} interface defines the \object{tokenize} method.
When appropriate, an interface defines \emph{extended action
  methods}, which provide variations on the basic action method.  For
example, the \object{ParserI} interface defines the \object{parse\_n}
method which finds at most $n$ parses for a given sentence; and
the \object{TokenizerI} interface defines the \object{xtokenize}
method, which outputs an iterator over subtokens instead of a list of
subtokens.

@@

NLTK is a broad-coverage toolkit that provides a simple, extensible,
uniform framework for assignments, demonstrations and projects.  It is
thoroughly documented, easy to learn, and simple to use.  Readers who
would like to receive occasional announcements about NLTK are
encouraged to sign up for the low-volume, moderated mailing list
\textit{NLTK-Announce}.\footnote{\url{http://lists.sourceforge.net/lists/listinfo/nltk-announce}}

@@

We are indebted to our students and colleagues for feedback on the
toolkit, and to many contributors listed on the NLTK website.
